EDA

### 2020-02-27 src/draft.Rmd
add acf, plus format modify

4. box plots of mill rates, grouped by region
```{r}
rate_boxes <- ggplot(dat_rate, aes(x=AddressAssessorMunicipalityDesc,y=rate,fill=TaxClassCode)) + geom_boxplot() + facet_wrap(~TaxClassCode) + theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
rate_boxes 
```
5. 
```{r}
#tax_final
#assessment_aggregate

@@

years <- c(2017, 2018, 2019)
city.cor <- data.frame(Municipality = municipality.list)
corr.list <- vector(length = 21)
corr.list
for(city in municipality.list){
  corr <- assessment_aggregate %>% filter(AddressAssessorMunicipalityDesc == city) %>% summarize(cor = cor(assessTotal, rate))
  #print(corr)
  corr.list <- cbind(corr.list, corr)
}
corr.list
city.cor <- cbind(city.cor,corr.list)
#city.cor

>>>>

4. box plots of mill rates, grouped by region
```{r}
rate_boxes <- ggplot(dat_rate, aes(x=AddressAssessorMunicipalityDesc,y=rate,fill=TaxClassCode)) + geom_boxplot() + facet_wrap(~TaxClassCode) + theme(axis.text.x = element_text(angle = 90, hjust = 1), legend.position = "none")
rate_boxes 
```

5. Test correlations between past mill rates and assessed values and government budget.
```{r}
#tax_final
#assessment_aggregate

@@

years <- c(2017, 2018, 2019)
city.cor <- data.frame(Municipality = municipality.list)
corr.list <- vector(length = 21)
corr.list
for(city in municipality.list){
  corr <- assessment_aggregate %>% filter(AddressAssessorMunicipalityDesc == city) %>% summarize(cor = cor(assessTotal, rate))
  #print(corr)
  corr.list <- cbind(corr.list, corr)
}
corr.list
city.cor <- cbind(city.cor,corr.list)
#city.cor
```

6. Compute autocorrelations of past mill rates to test the independence of mill rates. 
```{r}
# all white noise
for (i in 1:21) {
  print(municipality.list[i])
  dat_tmp <- dat_rate %>% filter(AddressAssessorMunicipalityDesc %in% municipality.list[i] & TaxClassCode %in% "1") %>% select(rate)
  if (municipality.list[i] != "Maple Ridge Rural") {
    as.ts(dat_tmp)
    acf(dat_tmp)
  }
}
for (i in 1:21) {
  print(municipality.list[i])
  dat_tmp <- dat_rate %>% filter(AddressAssessorMunicipalityDesc %in% municipality.list[i] & TaxClassCode %in% "5") %>% select(rate)
  if (municipality.list[i] != "Maple Ridge Rural" & municipality.list[i] != "White Rock" & municipality.list[i] != "Anmore" & municipality.list[i] != "Belcarra" & municipality.list[i] != "Lions Bay") {
    as.ts(dat_tmp)
    acf(dat_tmp)
  }
}
for (i in 1:21) {
  print(municipality.list[i])
  dat_tmp <- dat_rate %>% filter(AddressAssessorMunicipalityDesc %in% municipality.list[i] & TaxClassCode %in% "6") %>% select(rate)
  if (municipality.list[i] != "Maple Ridge Rural") {
    as.ts(dat_tmp)
    acf(dat_tmp)
  }
}
```
